### 2025-06-19 simulation.qmd
20250619 - fix

```{r}
Analyse <- function(condition, dat, fixed_objects = NULL) {
  tibble::tibble(
    id        = condition$id,
    mean_pts  = mean(dat$sim_points, na.rm = TRUE),
    sd_pts    = sd(dat$sim_points, na.rm = TRUE),
    q10       = quantile(dat$sim_points, 0.10, na.rm = TRUE),
    q90       = quantile(dat$sim_points, 0.90, na.rm = TRUE),
    p100      = mean(dat$sim_points >= 100, na.rm = TRUE),
    p150      = mean(dat$sim_points >= 150, na.rm = TRUE),
    p200      = mean(dat$sim_points >= 200, na.rm = TRUE),
    p250      = mean(dat$sim_points >= 250, na.rm = TRUE),
    p300      = mean(dat$sim_points >= 300, na.rm = TRUE),
    p350      = mean(dat$sim_points >= 300, na.rm = TRUE)
  )
}
```

@@

@@

>>>>

```{r}
Analyse <- function(condition, dat, fixed_objects = NULL) {
  tibble::tibble(
    id        = condition$id,
    mean_pts  = mean(dat$sim_points, na.rm = TRUE),
    sd_pts    = sd(dat$sim_points, na.rm = TRUE),
    q10       = quantile(dat$sim_points, 0.10, na.rm = TRUE),
    q90       = quantile(dat$sim_points, 0.90, na.rm = TRUE),
    p100      = mean(dat$sim_points >= 100, na.rm = TRUE),
    p150      = mean(dat$sim_points >= 150, na.rm = TRUE),
    p200      = mean(dat$sim_points >= 200, na.rm = TRUE),
    p250      = mean(dat$sim_points >= 250, na.rm = TRUE),
    p300      = mean(dat$sim_points >= 300, na.rm = TRUE),
    p350      = mean(dat$sim_points >= 350, na.rm = TRUE)
  )
}
```

@@

load(file = "./data/monteCarloSim_results.RData")
```

@@

The `pX` variable represent the probability that a player scoring more than X number of points.
For example, the `p300` variable represents the probability that each player scores more than 300 points.
However, it is important to note that this is based on the distribution of *projected* points.
